Linked Open Social Data for Scientific Benchmarking (Supporting Information document)

### 2016-07-26 supportingInformation.tex
mainly advances in description of supporting information diagrams

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%
\makeatletter
\def\ps@pprintTitle{%
    \let\@oddhead\@empty
    \let\@evenhead\@empty
    \def\@oddfoot{}%
\let\@evenfoot\@oddfoot}
\makeatother
\begin{document}
%
\begin{frontmatter}
%
\title{Linked Open Social Data for Scientific Benchmarking (Supporting
Information document)}
%
\author[pwr]{Renato Fabbri\corref{corresponding}\fnref{kio-url}}
\ead{fabbri@usp.br}
%
\author[pwr]{Osvaldo Novais de Oliveira Junior\fnref{kio-url}}
\ead{chu@ifsc.usp.br}
%
\cortext[corresponding]{Corresponding author}
\address[pwr]{S\~ao Carlos Institute of Physics, S\~ao Paulo
University, Brazil}
%
\fntext[kio-url]{\textit{URL:} \url{http://www.ifsc.usp.br/}}
%
\begin{abstract}
This is a Supporting Information document which exposes ontological
diagrams and auxiliary tables for the Linked Open Social Data (LOSD)
database. The main article is in~\cite{losd}.
\end{abstract}
%
\begin{keyword}
Big Data, Data Mining, Benchmark Data, Facebook, Twitter, IRC, Email, Complex Networks
%Hierarchy of Clusters \sep HoC \sep Benchmark Dataset \sep Benchmark Data Generator \sep Artificial Data \sep Cluster Analysis \sep Tree Structured Stick Breaking Process \sep TSSB \sep ...
\end{keyword}

\end{frontmatter}
\pdfpageheight 8in
\tableofcontents
\section{General guidance}
In this document we provide diagrams
the provenances in the LOSD:
Facebook, Twitter, IRC, Email, ParticipaBR, Cidade Democrática and AA.
Each provenance diagram was broken in two, one present the relations
among main classes and datatypes, the other present metadata on the
snapshot.

Furthermore, this document ends with two sets of tables, one with countings of
triples, participants, edges/interactions/relations and characters,
the other with references for snapshot groups, such as wikipedia or
contact links.

\section{Facebook data}

@@

\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Twitter};}
    paper=graphics
][scale=.5]{ontologies/twitter-legacy-arenaNETmundialMeta.ttl/draw.png}

@@

\section{Email data}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.4]{ontologies/gmane-legacy-.linux.audio.devel1-20000Email00000.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.5]{ontologies/gmane-legacy-.linux.audio.devel1-20000Meta.ttl/draw.png}

>>>>

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%
\makeatletter
\def\ps@pprintTitle{%
    \let\@oddhead\@empty
    \let\@evenhead\@empty
    \def\@oddfoot{}%
\let\@evenfoot\@oddfoot}
\makeatother
\begin{document}
%
\begin{frontmatter}
%
\title{Linked Open Social Data for Scientific Benchmarking (Supporting
Information document)}
%
\author[pwr]{Renato Fabbri\corref{corresponding}\fnref{kio-url}}
\ead{fabbri@usp.br}
%
\author[pwr]{Osvaldo Novais de Oliveira Junior\fnref{kio-url}}
\ead{chu@ifsc.usp.br}
%
\cortext[corresponding]{Corresponding author}
\address[pwr]{S\~ao Carlos Institute of Physics, S\~ao Paulo
University, Brazil}
%
\fntext[kio-url]{\textit{URL:} \url{http://www.ifsc.usp.br/}}
%
\begin{abstract}
This is a Supporting Information document which exposes ontological
diagrams and auxiliary tables for the Linked Open Social Data (LOSD)
database. The main document of the article is in~\cite{losd}.
\end{abstract}
%
\begin{keyword}
Big Data, Data Mining, Benchmark Data, Facebook, Twitter, IRC, Email,
Complex Networks, Text Mining
%Hierarchy of Clusters \sep HoC \sep Benchmark Dataset \sep Benchmark Data Generator \sep Artificial Data \sep Cluster Analysis \sep Tree Structured Stick Breaking Process \sep TSSB \sep ...
\end{keyword}

\end{frontmatter}
% \pdfpageheight 8in
\tableofcontents
\section{General guidance}
% \paperheight = 200pt
In this document we provide diagrams
for the provenances in the LOSD:
Facebook, Twitter, IRC, Email, ParticipaBR, Cidade Democrática and AA.
Each provenance diagram was broken in two, one presents the relations
among main classes (blue nodes) and data types (orange nodes), the other presents metadata on the
snapshot.
Every class instance is related to the snapshot instance
by the triple \textttt{class\_uri po:snapshot snapshot\_uri}.
Such triples are omitted for simplicity.
Due to the large number of relations, the rendering of diagrams are
automatized and displays imperfections.
Even so, the images are useful for grasping what is in current LOSD
and for conducting explorations.
Edges in the diagrams have:
\begin{itemize}
    \item green color if representing an OWL existential
class restriction (all individuals from the class present at least one triple with
the property as predicate);
    \item inverted nip if representing an OWL universal class
        restriction (all individuals presenting triples with the
        property as predicate are from the class);
    \item full edges (non-dashed) if representing a functional property
        axiom (there is at most one triple with the property as the
        predicate for each individual).
\end{itemize}

% \textheight = 100pt
% \pdfpageheight 300pt
Furthermore, this document ends with two sets of tables, one with counts of
triples, participants, edges/interactions/relations and characters,
the other with references for snapshot groups, such as wikipedia or
contact links.

\section{Facebook data}
Each Facebook snapshot is yield through either an user, from which the
friends constitute a friendship network, or a group, which participants
can yield friendship and interaction networks and posts information with
text and some metadata.
Further information is found on the following diagrams, the tables on
the end of this document or in the main document of this
article~\cite{losd}.

@@

\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Twitter};}
    paper=graphics
][scale=.7]{ontologies/twitter-legacy-arenaNETmundialMeta.ttl/draw.png}

@@

\section{Email data}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.4]{ontologies/gmane-legacy-.linux.audio.devel1-20000Email00000.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.5]{ontologies/gmane-legacy-linux.audio.devel1-20000Meta.ttl/draw.png}
